Sardines only end-to-end atlantisom test

### 2019-06-06 SardinesOnlyatlantisom2SStest.Rmd
still broken

>>>>

Sadly, still a problem with the catch correction if it should match catch.txt when comverted to biomass. We are now off by about a factor of 2 (catch nums * wtAtAge is half true catch bio from the txt file):

```{r catchoff}
sardcatchB <- truecatchbio_ss %>%
  mutate(yr = as.integer(time/365))

sardcatchBcomp <- merge(sardcatchB, catchbioN_ss)
sardcatchBcomp <- mutate(sardcatchBcomp, mult=atoutput/anncatchB)

mean(sardcatchBcomp$mult)

summary(sardcatchBcomp$mult)
